---
title: "Calfee/Matthay Lab Inventory QC"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(redcapAPI)
library(tidyverse)
library(lubridate)
library(readxl)
library(kableExtra)

#REDCAP API
redcap_url = "https://redcap.ucsf.edu/api/"
token = "DB07D345FD21242AACB7964924EC0D70"                             
rcon_lims = redcapConnection(url = redcap_url, token = token)

redcap_export <- exportRecords(rcon = rcon_lims, form = "sample_storage")
```

\newpage

# Duplicated Sample IDs

## Check for same sample ID being uploaded multiple times within a study

```{r Duplicated Sample IDs}

#Function for identifying and outputting a table of duplicates sample IDs within a study
duplicated_samples <- function(study, event_name){
  #Filter for specific study using event name given
  study_filtered <- redcap_export %>% filter(redcap_event_name == event_name) 
  
  #Find duplicated sample IDs
  duplicates <- study_filtered %>% group_by(sample_id) %>%
    tally() %>%
    filter(n > 1)
  
  #Filter original study specific data for only the identified duplicated IDs
  study_duplicates_only <- study_filtered %>% filter(sample_id %in% duplicates$sample_id) %>%
    select(record_id,sample_id,container_type:freezer_shelf_number)

  #Output table of duplicates
  study_duplicates_only %>% kable(format = "html", booktabs = TRUE, linesep = "", caption = paste0(study," duplicated aliquot ids")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
}

#Plug in study name and event name
duplicated_samples("Comet","comet_arm_2")
duplicated_samples("Earli","earli_arm_3")

```


\newpage

# Grid Position Check

## Checks for duplicated grid position within a box as well as grid positions that are not possible based on box dimensions

```{r Grid Position Duplicates/ Out of Range}

#Function for identifying and outputting a table of duplicated grid locations
grid_position_check <- function(study, event_name){
  
  #Filter for specific study using event name given,status is stored
  study_filtered <- redcap_export %>% filter(redcap_event_name == event_name, sample_status %in% c("Stored","Hold")) 
  
  #Find duplicated grid location within a container
  duplicates <- study_filtered %>% filter(!is.na(grid_position)) %>%
    group_by(container_matthay_lab_id, grid_position) %>%
    tally() %>%
    filter(n > 1) %>%
    mutate(exact_location = str_c(container_matthay_lab_id,grid_position, sep = "_"))
  
  #Filter original study specific data for only the identified duplicated IDs
  study_duplicates_only <- study_filtered %>% mutate(exact_location = str_c(container_matthay_lab_id,grid_position, sep = "_")) %>%
    filter(exact_location %in% duplicates$exact_location) %>%
    select(record_id,sample_id,container_type:freezer_shelf_number) %>%
    arrange(container_matthay_lab_id,grid_position)
  
  #Output table of duplicates
  study_duplicates_only %>% kable(format = "html", booktabs = TRUE, linesep = "", caption = paste0(study," duplicated aliquot ids"))%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
  
  
  
}


#Function to check for out of range grid location
grid_range_check <- function(study, event_name){
  #Filter for specific study using event name given, status is stored
  study_filtered <- redcap_export %>% filter(redcap_event_name == event_name, sample_status %in% c("Stored","Hold")) 
  
  #Range check for each type of box
  range_check <- study_filtered %>% mutate(in_range = case_when(container_type == "Plastic box (5x10)" & grid_position > 50 ~ "Out",
                                                                container_type == "Plastic box (10x10)" & grid_position > 100 ~ "Out",
                                                                container_type == "96-Well Box" & grid_position > 96 ~ "Out",
                                                                (container_type == "Plastic Box (9x9)" | container_type == "Cardboard box (9x9)") & grid_position > 81 ~ "Out",
                                                                container_type == "Cardboard box (4x4)" & grid_position > 16 ~ "Out",
                                                                container_type == "Cardboard box (6x6)" & grid_position > 36 ~ "Out",
                                                                container_type == "Cardboard box (8x8)" & grid_position > 64 ~ "Out")) %>%
    filter(in_range == "Out") %>%
    select(record_id,sample_id,container_type:freezer_shelf_number,in_range)
  
  range_check %>% kable(format = "html", booktabs = TRUE, linesep = "", caption = paste0(study," grid range check"))%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
}

#Plug in study name and event name
grid_position_check("Comet","comet_arm_2")
grid_position_check("Earli","earli_arm_3")


grid_range_check("Comet","comet_arm_2")
grid_range_check("Earli","earli_arm_3")


```



\newpage

# Box Check

## Check that box information is stored consistently: container type is the same for each entry and freezer storage location

```{r Container Type and Freezer Location Continuity}

container_contradictions <- function(study, event_name){
  
  #Filter for specific study using event name given
  study_filtered <- redcap_export %>% filter(redcap_event_name == event_name, sample_status %in% c("Stored","Hold"))

  box_breakdown <- study_filtered %>% group_by(container_matthay_lab_id,container_type,freezer_number,freezer_shelf_number) %>%
    tally(name = "Samples Logged")

  box_multiple <- box_breakdown %>% group_by(container_matthay_lab_id) %>%
    tally() %>%
    filter(n > 1)

  box_contradictions <- box_breakdown %>% filter(container_matthay_lab_id %in% box_multiple$container_matthay_lab_id) 
  
  box_contradictions %>% kable(format = "html", booktabs = TRUE, linesep = "", caption = paste0(study," container contradictions")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
}

container_contradictions("COMET", "comet_arm_2")
container_contradictions("Earli", "earli_arm_3")


```



```{r Missing Data}

```

```{r Fixes, eval = FALSE}

samples_missing_freezer <- read_csv("~/Desktop/Earli Scanning 10_8_21.csv")
samples_missing_freezer <- samples_missing_freezer %>% filter(!is.na(sample_id))

redcap_export <- redcap_export %>% filter(sample_id %in% samples_missing_freezer$sample_id) %>%
  mutate(freezer_number = 7,
         freezer_shelf_number = 1,
         date_stored = "10/8/21",
         stored_by = "CL") %>%
  select(record_id,redcap_event_name,sample_id,freezer_number:stored_by) 

write_excel_csv(redcap_export,"freezer_info_add.csv",na = "")
```

